RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-14 main.tex
:bento: Update assets
:pencil: Add initialization and convergence discussion

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}

@@

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                       & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                     & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                     & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

	% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
	% TODO cooperative input design can be used for co-located RIScatter nodes.
	% TODO hardward to modulate using RIS is already available.
	% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
	% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
	% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
	% TODO Redefine RIS using book
	% TODO Using RIS to encode is not very interesting as controller is anyway usable
	% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
	% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
	% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
	% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
	% TODO convergence
	% TODO channel coding: general non-adaptive (book) adaptive (DMC)
	% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
	% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
	% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
	% TODO semicoherent: known CSI, unknown primary/backscatter symbols

@@

		\emph{Fourth,} we characterize the achievable primary-total-backscatter rate region of the aforementioned system by optimizing the input distribution, active beamforming, and backscatter decision regions.
		It is formulated as a weighted sum-rate maximization subject to input probability simplex, average transmit power, and sequential decision threshold constraints.
		Since the original problem is highly non-convex, we decouple it into individual subproblems and constraint all decision regions to convex (connected) intervals.
		A suboptimal \gls{bcd} algorithm is then proposed, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are refined by existing thresholding designs.

@@

		Conditioned on backscatter index tuple $m_{\mathcal{K}}$, the received signal \eqref{eq:receive_signal} follows \gls{cscg} distribution $y[n] \sim \mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where

@@

		Besides, we define the total received energy per backscatter block as $z=\sum_{n=1}^N \lvert y[n] \rvert^2$.

@@

		The \gls{pgd} active beamforming optimization with step size determined by backtracking line search is summarized in Algorithm \ref{al:active_beamforming}.
		\begin{algorithm}[!t]
			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with Backtracking Line Search}
			\label{al:active_beamforming}
			\begin{algorithmic}[1]
				\Require $Q$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
				\Ensure $\boldsymbol{w}^\star$
				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}
					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
					\EndWhile
					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
	\end{equation}
	together with a Ricean fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.

>>>>

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
\newacronym{bls}{BLS}{Backtracking Line Search}

@@

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (?ly collaborative)                        & 1                                       & 2 (adaptively collaborative)                      \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                     & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                     & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

	% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
	% TODO cooperative input design can be used for co-located RIScatter nodes.
	% TODO hardward to modulate using RIS is already available.
	% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
	% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
	% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
	% TODO Redefine RIS using book
	% TODO Using RIS to encode is not very interesting as controller is anyway usable
	% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
	% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
	% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
	% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
	% TODO convergence
	% TODO channel coding: general non-adaptive (book) adaptive (DMC)
	% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
	% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
	% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
	% TODO semicoherent: known CSI, unknown primary/backscatter symbols
	% TODO initialization, convergence

@@

		\emph{Fourth,} we characterize the achievable primary-total-backscatter rate region of the aforementioned system by optimizing the input distribution, active beamforming, and backscatter decision regions.
		It is formulated as a weighted sum-rate maximization subject to input probability simplex, average transmit power, and sequential decision threshold constraints.
		Since the original problem is highly non-convex, we decouple it into individual subproblems and constraint all decision regions to convex (connected) intervals.
		A suboptimal \gls{bcd} algorithm is then proposed, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by \gls{bls}, and the decision regions are refined by existing thresholding designs.

@@

		Conditioned on backscatter index tuple $m_{\mathcal{K}}$, the received signal at each primary block follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$, where

@@

		Besides, we define the total received energy per backscatter block as $z=\sum_{n \in \mathcal{N}} \lvert y[n] \rvert^2$.

@@

		The \gls{pgd} active beamforming optimization with step size determined by \gls{bls} is summarized in Algorithm \ref{al:active_beamforming}.
		\begin{algorithm}[!t]
			\caption{Iterative Active Beamforming Optimization by \gls{pgd} with \gls{bls}}
			\label{al:active_beamforming}
			\begin{algorithmic}[1]
				\Require $Q$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
				\Ensure $\boldsymbol{w}^\star$
				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}
					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
					\EndWhile
					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{1000} realizations, and the parameters remain fixed unless otherwise specified.

	\begin{subsection}{Evaluation of Algorithms}
		\begin{subsubsection}{Initialization}
			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing the primary priority $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
			At $\rho=0$ where backscatter performance is absolutely prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards sum cascaded channel $\sum_{k \in \mathcal{K}} \boldsymbol{h}_{\mathrm{C},k}^H$, respectively.
			At the following points, both algorithms are initialized by the solutions of the previous point.
		\end{subsubsection}

		\begin{subsubsection}{Convergence}
			\begin{figure}[!t]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\input{assets/simulation/wsr_convergence.tex}
				}
				\caption{Convergence behavior of the proposed algorithms for $\rho=0$.}
				\label{fi:wsr_convergence}
			\end{figure}

			In Fig. \ref{fi:wsr_convergence}, we plot the weighted sum of primary and total backscatter rates for \gls{kkt}, \gls{pgd} (on the first call within \gls{bcd}) and \gls{bcd} algorithms in each iteration at $\rho=0$.
			For $K=8$ and $M=2$, Algorithm \ref{al:input_distribution} typically takes around \num{100} fast iterations based on \eqref{eq:input_kkt_solution} to converge to the \gls{kkt} input distribution.
			For $Q=4$, around \num{10} iterations are required for Algorithm \ref{al:active_beamforming} to converge, where the gradient needs to be evaluated by \eqref{eq:weighted_sum_mutual_information_gradient} and the step size needs to be refined by \gls{bls}.
			The \gls{bcd} algorithm typically takes around \num{5} iterations to converge.
			At the following points (not shown here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
			Overall, we conclude the proposed algorithms are able to converge within moderate iterations and provide significant rate gains for the RIScatter system.
		\end{subsubsection}
	\end{subsection}

	\begin{subsection}{Comparison of Scattering Applications}
		% AmBC: co-located non-cooperative receivers, use SINR to evaluate primary rate even if backscatter symbols are not Gaussian distributed
		% For a fair comparison, we employ energy-based backscatter detection for scattering applications evaluated in this subsection.
		% For a fair comparison, we evaluate different scattering applications with backscatter energy detection over the setup in Fig. \ref{fi:riscatter_network}.
		For a fair comparison, we employ backscatter energy detection for these scattering applications over the setup in Fig. \ref{fi:riscatter_network}:
		% employ energy-based backscatter detection for scattering applications evaluated in this subsection.
		\begin{itemize}
			\item \emph{\gls{bbc}:}
			% The \gls{ap} becomes carrier emitter and the user becomes backscatter reader.
			The primary symbol $s[n]$ becomes deterministic and the receive signal at each primary block is
				y^{\text{\gls{bbc}}}[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} + v[n],
			% which follows non-zero mean complex Gaussian distribution $y_{m_{\mathcal{K}}}^{\text{BBC}}[n] \sim \mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
			which follows non-zero mean complex Gaussian distribution $\mathcal{CN}\bigl(\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w},\sigma_v^2\bigr)$ under hypothesis $\mathcal{H}_{m_{\mathcal{K}}}$.
			% The corresponding \gls{pdf} of receive energy over $N$ primary blocks is
			The corresponding \gls{pdf} of accumulated receive energy over $N$ primary blocks is
				f^{\text{\gls{bbc}}}(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{(z-\mu_{m_{\mathcal{K}}})^{N-1} \exp(-(z-\mu_{m_{\mathcal{K}}})/\sigma_v^2)}{\sigma_v^{2N} (N-1)!},
			where $\mu_{m_{\mathcal{K}}} \triangleq N \lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2$.
			\item \emph{\gls{ambc}:} The user decodes both links independently and semi-coherently by treating the other as interference or uncertainty.
			% Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the interference from finite-input backscatter sources by those from independent Gaussian sources.}
			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we approximate the scattered signal components from finite-input backscatter sources by independent interference from Gaussian sources.}
